\mireval{}:\\ A Transparent Implementation of Common MIR Metrics

### 2014-07-16 paper/paper.tex
Author edits thanks to @ejhumphrey
Camera ready

@@

\author[1]{Colin Raffel}
\author[1,2]{Brian McFee}
\author[3]{Eric J. Humphrey}
\author[3,4]{Justin Salamon}
\author[3]{Oriol Nieto}
\author[1]{Dawen Liang}
\author[1]{Daniel P. W. Ellis}
\affil[1]{LabROSA, Dept.~of Electrical Engineering\\Columbia University, New York}
\affil[2]{Center for Jazz Studies\\Columbia University, New York}
\affil[3]{Music and Audio Research Lab\\New York University, New York}
\affil[4]{Center for Urban Science and Progress\\New York University, New York}

@@

\begin{document}
%
\maketitle
%
\begin{abstract}
Central to the field of MIR research is the evaluation of algorithms used to extract information from music data.
We present \mireval{}, an open source software library which provides a transparent and easy-to-use implementation of the most common metrics used to measure the performance of MIR algorithms.
In this paper, we enumerate the metrics implemented by \mireval{} and quantitatively compare each to  existing implementations.
When the scores reported by \mireval{} differ substantially from the reference, we detail the differences in implementation.
We also provide a brief overview of \mireval{}'s architecture, design, and intended use.
\end{abstract}
%
\section{Evaluating MIR Algorithms}

@@

Collins compiled all previously existent metrics and proposed novel ones~\cite{Collins2013} which resulted in 19 different scores, each one implemented in \mireval{}:
\textbf{Standard F-measure, Precision, and Recall}, where an estimated prototype pattern is considered correct only if it matches (up to translation) a reference prototype pattern;
\textbf{Establishment F-measure, Precision, and Recall}, which computes the number of reference patterns that were successfully found, no matter how many occurrences were found;
\textbf{Occurrence F-measure, Precision, and Recall}, which measures whether an algorithm is able to retrieve all occurrences of a pattern;
\textbf{Three-layer F-measure, Precision, and Recall}, which capture both the establishment of the patterns and the occurrence retrieval in a single set of scores;
and the \textbf{First $N$ patterns metrics}, which computes the target proportion establishment recall and three-layer precision for the first $N$ patterns only in order to measure the ability of the algorithm to sort the identified patterns based on their relevance.

@@

The Information Gain metric~\cite{davies2009evaluation} involves the computation a histogram of the per-beat errors.
The Beat Evaluation Toolbox (and therefore MIREX) uses a non-uniform histogram binning where the first, second and last bins are smaller than the rest of the bins while \mireval{} uses a standard uniformly-binned histogram.
As a result, the Information Gain score reported by \mireval{} differs substantially from that reported by MIREX.

>>>>

\renewcommand\Authfont{\bfseries}

@@

\author[1,*]{Colin Raffel}
\author[1,2]{Brian McFee}
\author[3]{Eric J. Humphrey}
\author[3,4]{Justin Salamon}
\author[3]{Oriol Nieto}
\author[1]{\authorcr Dawen Liang}
\author[1]{Daniel P. W. Ellis}
\affil[1]{LabROSA, Dept.~of Electrical Engineering\\Columbia University, New York}
\affil[2]{Center for Jazz Studies\\Columbia University, New York}
\affil[3]{Music and Audio Research Lab\\New York University, New York}
\affil[4]{Center for Urban Science and Progress\\New York University, New York}

@@

\begin{document}
%
\maketitle

\let\oldthefootnote\thefootnote
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\footnotetext[1]{Please direct correspondence to \url{craffel@gmail.com}}
\let\thefootnote\oldthefootnote

%
\begin{abstract}
Central to the field of MIR research is the evaluation of algorithms used to extract information from music data.
We present \mireval{}, an open source software library which provides a transparent and easy-to-use implementation of the most common metrics used to measure the performance of MIR algorithms.
In this paper, we enumerate the metrics implemented by \mireval{} and quantitatively compare each to  existing implementations.
When the scores reported by \mireval{} differ substantially from the reference, we detail the differences in implementation.
We also provide a brief overview of \mireval{}'s architecture, design, and intended use.
\end{abstract}
%
\section{Evaluating MIR Algorithms}

@@

Collins compiled all previously existent metrics and proposed novel ones~\cite{Collins2013} which resulted in 19 different scores, each one implemented in \mireval{}:
\textbf{Standard F-measure, Precision, and Recall}, where an estimated prototype pattern is considered correct only if it matches (up to translation) a reference prototype pattern;
\textbf{Establishment F-measure, Precision, and Recall}, which compute the number of reference patterns that were successfully found, no matter how many occurrences were found;
\textbf{Occurrence F-measure, Precision, and Recall}, which measure whether an algorithm is able to retrieve all occurrences of a pattern;
\textbf{Three-layer F-measure, Precision, and Recall}, which capture both the establishment of the patterns and the occurrence retrieval in a single set of scores;
and the \textbf{First $N$ patterns metrics}, which compute the target proportion establishment recall and three-layer precision for the first $N$ patterns only in order to measure the ability of the algorithm to sort the identified patterns based on their relevance.

@@

The Information Gain metric~\cite{davies2009evaluation} involves the computation of a histogram of the per-beat errors.
The Beat Evaluation Toolbox (and therefore MIREX) uses a non-uniform histogram binning where the first, second and last bins are smaller than the rest of the bins while \mireval{} uses a standard uniformly-binned histogram.
As a result, the Information Gain score reported by \mireval{} differs substantially from that reported by MIREX.
